Diversification of salmon fishermen within strategies (permits)

### 2016-08-11 salmon/analysis/salmon_paper.Rmd
final version to send out
added code for residual plots

---
title: "Diversification of salmon fishermen within strategies (permits)"
author: ""
date: ""
output:
  pdf_document:
    fig_caption: yes
  html_document: default
---

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
dat.annual = readRDS(file="../../portfolio/data-generated/cfec-annual-for-modeling.rds")

@@

dat.diff = readRDS(file="../../portfolio/data-generated/cfec-diff-for-modeling.rds")
dat.diff = dat.diff[which(dat.diff$revenue >= 5000 & dat.diff$revenue.prev >= 5000), ]
dat.diff = dat.diff[dat.diff$strategy_permit%in%c("S01A","S01E","S01K","S01L","S01M",
  "S03A","S03E","S03H","S03M","S03T","S04D","S04H","S04K","S04M","S04T"),]

@@

@@

Revenue is going up since 2000 -- but each permit holder is fishing more (more days, more total pounds) and the trend in weight is faster than the trend in price.  
```{r, echo=FALSE, fig.height = 3.5, fig.cap="Trends in average landed weight per person", fig.pos="placeHere"}
group_by(cfec, p_fshy, year, p_holder) %>% 
  summarize(meanW = mean(g_pounds/2000, na.rm=T)) %>% 
  group_by(p_fshy, year) %>% 
  summarize(meanW = mean(meanW, na.rm=T)) %>% 
  ggplot(aes(year, meanW)) + geom_line() + facet_wrap(~ p_fshy, scale="free") + ylab("Mean total tons per person") + xlab("Year") + ggtitle("Trends in landed weight")
```

>>>>

---
title: "Diversification of salmon fishermen within strategies (permits)"
author: ''
date: ''
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document: default
---

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
revenueThreshold = 10000

dat.annual = readRDS(file="../../portfolio/data-generated/cfec-annual-for-modeling.rds")

@@

dat.diff = readRDS(file="../../portfolio/data-generated/cfec-diff-for-modeling.rds")
dat.diff = dat.diff[which(dat.diff$revenue >= revenueThreshold & dat.diff$revenue.prev >= revenueThreshold), ]
dat.diff = dat.diff[dat.diff$strategy_permit%in%c("S01A","S01E","S01K","S01L","S01M",
  "S03A","S03E","S03H","S03M","S03T","S04D","S04H","S04K","S04M","S04T"),]

@@

```{r, echo = FALSE}
pdf("Salmon_residuals.pdf")
# Residuals for mean model
dat.salmon$mu.resid = residuals(mu.mod)
dat.salmon$mu.fitted = fitted(mu.mod)

ggplot(dat.salmon, aes(mu.fitted, mu.resid, group = strategy_permit)) + geom_point() + facet_wrap(~strategy_permit) + xlab("Fitted") + ylab("Residuals") + ggtitle("Mean model")
ggplot(dat.salmon, aes(specDiv.change, mu.resid, group = strategy_permit)) + geom_point() + facet_wrap(~strategy_permit) + xlab("Change in species diversification") + ylab("Residuals") + ggtitle("Mean model") + geom_hline(aes(yintercept=0),color="salmon1")
ggplot(dat.salmon, aes(specdiv.prev, mu.resid, group = strategy_permit)) + geom_point() + facet_wrap(~strategy_permit) + xlab("Previous species diversity") + ylab("Residuals") + ggtitle("Mean model") + geom_hline(aes(yintercept=0),color="salmon1")
ggplot(dat.salmon, aes(log((revenue+revenue.prev)/2), mu.resid, group = strategy_permit)) + geom_point() + facet_wrap(~strategy_permit) + xlab("Average revenue") + ylab("Residuals") + ggtitle("Mean model") + geom_hline(aes(yintercept=0),color="salmon1")

# Residuals for CV model
dat.salmon$cv.resid = residuals(cv.mod)
dat.salmon$cv.fitted = fitted(cv.mod)

ggplot(dat.salmon, aes(cv.fitted, cv.resid, group = strategy_permit)) + geom_point() + facet_wrap(~strategy_permit) + xlab("Fitted") + ylab("Residuals") + ggtitle("CV model")
ggplot(dat.salmon, aes(specDiv.change, cv.resid, group = strategy_permit)) + geom_point() + facet_wrap(~strategy_permit) + xlab("Change in species diversification") + ylab("Residuals") + ggtitle("CV model") + geom_hline(aes(yintercept=0),color="salmon1")
ggplot(dat.salmon, aes(specdiv.prev, cv.resid, group = strategy_permit)) + geom_point() + facet_wrap(~strategy_permit) + xlab("Previous species diversity") + ylab("Residuals") + ggtitle("CV model") + geom_hline(aes(yintercept=0),color="salmon1")
ggplot(dat.salmon, aes(log((revenue+revenue.prev)/2), cv.resid, group = strategy_permit)) + geom_point() + facet_wrap(~strategy_permit) + xlab("Average revenue") + ylab("Residuals") + ggtitle("CV model") + geom_hline(aes(yintercept=0),color="salmon1")
dev.off()
```

@@

Revenue is going up since 2000 -- but each permit holder is fishing more (more days, more total pounds) and the trend in weight is faster than the trend in price.

```{r, echo=FALSE, fig.height = 3.5, fig.cap="Trends in average landed weight per person", fig.pos="placeHere"}
group_by(cfec, p_fshy, year, p_holder) %>% 
  summarize(meanW = mean(g_pounds/2000, na.rm=T)) %>% 
  group_by(p_fshy, year) %>% 
  summarize(meanW = mean(meanW, na.rm=T)) %>% 
  ggplot(aes(year, meanW)) + geom_line() + facet_wrap(~ p_fshy, scale="free") + ylab("Mean total tons per person") + xlab("Year") + ggtitle("Trends in landed weight")
```
